---
title: "Pharmacokinetics of sufentanil after epidural administration"
author:   
  - Pawel Wiczling
  - Agnieszka Bienert
  - Paulina Okuńska
  - Agnieszka Borsuk-de Moor
  - Justyna Ber
date: today
date-format: long
format:
  html:
    toc: true
    code-fold: true
execute:
  warning: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=F, message=FALSE, error=FALSE, warning=FALSE, comment=NA, out.width='95%')
```

# Introduction

Pharmacokinetics of sufentanil after epidural administration.

```{r load-libraries}
library(pracma)
library(bbr)
library(bbr.bayes)
library(dplyr)
library(ggplot2)
library(patchwork)
library(mrgsolve)
library(vpc)
library(pmplots)
library(naniar)
library(knitr)
library(data.table)
library(tidyverse)
library(glue)
library(whisker)
library(here)
library(scales)
library(pmplots)
library(pmtables)
library(nmrec)
library(cmdstanr)
library(gridExtra)
library(posterior)
library(ggh4x)
library(loo)

set_cmdstan_path("C:/Users/GUMed/Documents/.cmdstan/Torsten-0.91.0/cmdstan")

#' helper functions
source(here::here("scripts","functions","functions-tables.R"))

# table summary 
sigfun = function(.x){sig(.x,digits=3)}

#for the future:
#remotes::install_github("metrumresearchgroup/nmrec")
#devtools::install_github("metrumresearchgroup/bbr", ref = "main")
# https://github.com/metrumresearchgroup/NMBayesTutorial/tree/main
thisScript <- "bayesian-analysis.qmd"

# cmdstanr::check_cmdstan_toolchain()
# rebuild_cmdstan(
#   dir = cmdstan_path(),
#   cores = getOption("mc.cores", 16),
#   quiet = FALSE,
#   timeout = 600)
```

# Settings
```{r settings}
data_dir <- here::here("data","derived") 
model_dir <- here::here("model","torsten")  
figures_dir <- here::here("deliv","figures", "torsten")
tables_dir <- here::here("deliv","tables", "torsten")
```

# Plotting functions
```{r ploting-functions}
#------------------------------------------------------------------------------
plot_param_tables <-function(mod_to_plot, pars){ 
  mod_to_plot$summary(c(pars)) %>%
  mutate_if(is.numeric, ~formatC(., 3)) %>% 
  rename(parameter = variable) %>%
  mutate("90% CI" = paste("(", q5, ", ", q95, ")", sep = "")) %>%
  select(parameter, mean, median, sd, mad, "90% CI", ess_bulk, ess_tail, rhat)%>%
  filter(str_detect(parameter, 
                    "\\[1,1\\]|\\[2,2\\]|\\[3,3\\]|\\[4,4\\]|\\[5,5\\]|\\[6,6\\]|\\[7,7\\]", negate = T))
}

#------------------------------------------------------------------------------
pred_by_id_fun <- function(mod_to_plot, xdata){
  
  predInd <-  posterior::as_draws_df(mod_to_plot$draws("cCond")) %>%
  pivot_longer(cols = starts_with("cCond"),
               names_transform = list(name = forcats::fct_inorder)) %>%
  group_by(name) %>%
  summarize(lbInd = quantile(value, probs = 0.05, na.rm = TRUE),
            medianInd = quantile(value, probs = 0.5, na.rm = TRUE),
            ubInd = quantile(value, probs = 0.95, na.rm = TRUE))

predPop <- posterior::as_draws_df(mod_to_plot$draws("cPred")) %>%
  pivot_longer(cols = starts_with("cPred"),
               names_transform = list(name = forcats::fct_inorder)) %>%
  group_by(name) %>%
  summarize(lbPop = quantile(value, probs = 0.05, na.rm = TRUE),
            medianPop = quantile(value, probs = 0.5, na.rm = TRUE),
            ubPop = quantile(value, probs = 0.95, na.rm = TRUE))

predAll <- bind_cols(xdata, predInd, predPop) %>%
  mutate(DV = if_else(EVID==0,DV, NA))

plot <- ggplot(predAll, aes(x = TIMEh, y = DV)) +
  geom_line(aes(x = TIMEh, y = medianPop, color = "population")) +
  geom_ribbon(aes(ymin = lbPop, ymax = ubPop, fill = "population"), alpha = 0.25) +
  geom_line(aes(x = TIMEh, y = medianInd, color = "individual")) +
  geom_ribbon(aes(ymin = lbInd, ymax = ubInd, fill = "individual"), alpha = 0.25) +
  scale_color_brewer(name  ="prediction",
                     breaks=c("individual", "population"),
                     palette = "Set1") +
  scale_fill_brewer(name  ="prediction",
                    breaks=c("individual", "population"),
                    palette = "Set1") +
  geom_point(na.rm = TRUE, size = 0.5) +
  scale_y_log10() +
  labs(x = "Time (h)",
       y = "Sufentanil concentrations, pg/ml") +
  theme(text = element_text(size = 8),
        axis.text = element_text(size = 8),
        legend.position = "bottom",
        strip.text = element_text(size = 8)) +
  coord_cartesian(ylim = c(0.1,200))+
  facet_wrap(~ ID)
  
plot
}

#------------------------------------------------------------------------------
vpc_fun <- function(mod_to_plot, xdata){

nPost <- mod_to_plot$metadata()$iter_sampling / mod_to_plot$metadata()$thin
n_chains <- 4

inf_labs <- c("TRUE" = "During infusion",
  "FALSE" = "Post infusion")
predPop <- posterior::as_draws_df(mod_to_plot$draws("cPred")) %>%
  pivot_longer(cols = starts_with("cPred"),
               names_transform = list(name = forcats::fct_inorder)) %>%
  mutate(ID = rep(xdata$ID, n_chains * nPost),
         TIME = rep(xdata$TIME, n_chains * nPost),
         CMT = rep(xdata$CMT, n_chains * nPost),
         EVID = rep(xdata$EVID, n_chains * nPost),
         infusion = rep(xdata$infusion, n_chains * nPost),
         DV = rep(xdata$DV, n_chains * nPost)) %>%
  filter(.iteration<=250)

sim <-predPop %>% filter(!is.na(DV)) %>% filter(EVID==0) %>% mutate(infusion = as.factor(infusion))
obs <- xdata %>% filter(!is.na(DV)) %>% filter(EVID==0) %>% mutate(infusion = as.factor(infusion))

vpc_plot <- vpc(sim = sim,
               obs = obs,
               obs_cols = list(id = "ID", dv = "DV", idv = "TIME"),
               sim_cols = list(is = "ID", dv = "value", idv = "TIME"),
               ci = c(0.1, 0.9), pi = c(0.1, 0.9),
               stratify = "infusion",
               bins = "jenks",
               log_y = T,
               log_y_min = 0.04,
               scales = "free_x",
               labeller = labeller(infusion = inf_labs),
               show = list(obs_dv = TRUE, obs_ci = TRUE, 
                           pi = FALSE, pi_as_area = FALSE, pi_ci = TRUE, 
                           obs_median = TRUE, sim_median = FALSE, sim_median_ci = TRUE),
               vpc_theme = new_vpc_theme(update = list(
                 sim_pi_fill = "snow4",
                 sim_pi_alpha = 0.25,
                 obs_ci_size = 1,
                 obs_ci_color = "snow4",
                 obs_median_color = "royalblue",
                 obs_ci_linetype = 1,
                 sim_median_fill = "royalblue",
                 sim_median_alpha = 0.25)))+theme_bw()

vpc_plot <- vpc_plot +
  labs(x = "Time (h)",
       y = "Sufentanil concentrations, pg/ml") 

vpc_plot
}

#------------------------------------------------------------------------------
gof_fun <- function(mod_to_plot, xdata){
yrepCond <- as_draws_matrix(mod_to_plot$draws(variables = c("cCond")))
yrepPred <- as_draws_matrix(mod_to_plot$draws(variables = c("cPred")))

 yobs <- xdata$DV
 ktore <- xdata$CMT==2 & xdata$EVID==0
 p1 <- bayesplot::ppc_intervals(y = 1000+yobs[ktore], yrep = yrepCond[,ktore], x = yobs[ktore]) + 
   xlab("Observed (ng/ml)") +
   ylab("Individual predictions (ng/ml)") +
   scale_y_log10(limits = c(0.1, 200)) + 
   scale_x_log10(limits = c(0.1, 200)) +
   theme(legend.position = "none") +
   geom_abline(intercept = 0, slope = 1, color="grey", linetype="dotted")
 p2 <-bayesplot::ppc_intervals(y = 1000+yobs[ktore], yrep = yrepPred[,ktore], x = yobs[ktore]) +
  xlab("Observed (ng/ml)") + 
   ylab("Population predictions (ng/ml)") +
   scale_y_log10(limits = c(0.1, 200)) +
   scale_x_log10(limits = c(0.1, 200)) +
  theme(legend.position = "none") +
  geom_abline(intercept = 0, slope = 1, color="grey", linetype="dotted")
 
plot_all <- (p1+p2)
plot_all
}

#------------------------------------------------------------------------------
fun_cont_cov<-function(cov,etaM){
p1<-ggplot(etaM, aes_string(x=gsub("//.*","",cov), y="medianInd")) + 
  geom_point()+
  geom_errorbar(aes(ymin=lbInd, ymax=ubInd), width=.2, position=position_dodge(0.05))+
  geom_hline(yintercept = 0, color="gray", linetype="dotted", size=1) + 
  labs(y="Etas",x=gsub(".*//","",cov))+
  facet_wrap(~type, scales = "free_y")
return(p1)
}

#------------------------------------------------------------------------------
fun_cat_cov<-function(cov,etaM){
p1<-ggplot(etaM, aes_string(x=gsub("//.*","",cov), y="medianInd")) + 
  geom_boxplot()+
  geom_jitter()+
  geom_hline(yintercept = 0, color="gray", linetype="dotted", size=1) + 
  labs(y="Etas",x=gsub(".*//","",cov))+
  facet_wrap(~type, scales = "free_y")
return(p1)
}

#------------------------------------------------------------------------------
extract_etas_fun <- function(mod_to_plot,xdata){
idata = xdata %>%
  distinct(ID,.keep_all = T)%>%
  select(ID,AGE,WT, SEX) %>% 
  mutate(i = 1:n()) %>%
  mutate(SEXF = if_else(SEX==1,"Male", "Female"))
  
etaM <-  posterior::as_draws_df(mod_to_plot$draws("etaM")) %>% 
  tidybayes::spread_draws(etaM[i,type])%>%
  mutate(etaM = log(etaM)) %>%
  group_by(i,type) %>%
  summarize(lbInd = quantile(etaM, probs = 0.05, na.rm = TRUE),
            medianInd = quantile(etaM, probs = 0.5, na.rm = TRUE),
            meanInd = mean(etaM, na.rm = TRUE),
            ubInd = quantile(etaM, probs = 0.95, na.rm = TRUE)) %>%
  mutate(type = case_when(
    type == "1" ~ "CL",
    type == "2" ~ "Q",
    type == "3" ~ "V1",
    type == "4" ~ "V2",
    type == "5" ~ "Ka",
    type == "6" ~ "Ka14",
    type == "7" ~ "Ka41"))%>%
  left_join(idata)
}
```

# Load data

```{r load-data}
eda_figures_dir <- here::here(figures_dir, "EDA")
eda_tables_dir <- here::here(tables_dir,"EDA")
dir.create(eda_figures_dir, recursive = T)
dir.create(eda_tables_dir, recursive = T)

xdata <- read.csv(here::here(data_dir, "nonmem_data_v02.csv"), na.strings='.')

xdata <- xdata %>%
  mutate(outliers = OUT,
         infusion = TIMEh<TINFS,
         timepostinf = TIMEh-TINFS)
```

# EDA
## Plot raw data
```{r plot-raw-data}
#' Some plots
#' 

plot1<-ggplot(data = subset(xdata, EVID == 0 & outliers==0 & infusion==1), aes(x = TIMEh, y = DV, group = ID)) + 
  geom_point() + 
  geom_line() + 
  geom_point(data = subset(xdata, EVID == 0 & outliers==1 & infusion==1), aes(x = TIMEh, y = DV, group = ID),colour = "red") + 
scale_y_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+
  ylab("Sufentanil concentrations, pg/ml") +
  xlab("Time after infusion start, h") + 
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")), 
        legend.text=element_text(size=6),
        legend.title =element_text(size=6))

plot2<-ggplot(data = subset(xdata, EVID == 0 & outliers==0 & infusion==0), aes(x = timepostinf, y = DV, group = ID)) + 
  geom_point() + 
  geom_line() + 
  geom_point(data = subset(xdata, EVID == 0 & outliers==1 & infusion==0), aes(x = timepostinf, y = DV, group = ID),colour = "red") + 
scale_y_continuous(limits = c(0.1, 100),
                   trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+
 ylab(element_blank()) +
  xlab("Time after infusion end, h")+
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")), 
        legend.text=element_text(size=6),
        legend.title =element_text(size=6))

plot12 <-plot1+plot2


plot2<-ggplot(data = subset(xdata, EVID==0 & outliers==0), aes(x = TIMEh, y = DV, color = factor(ID)),shape=21) + 
  geom_point() +
  geom_line()+ 
scale_y_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+
  ylab("Sufentanil concentrations, pg/ml") +
  xlab("Time after infusion start, days") + 
  labs(color = "ID")+
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")), 
        legend.text=element_text(size=6),
        legend.title =element_text(size=6)) + 
  geom_segment(aes(x = 0, y = 100, xend = TINFS, yend = 100))+
  facet_wrap(.~factor(ID),nrow = 3)+
  theme(legend.position="none")


ggsave(filename = here::here(eda_figures_dir, "rawdata1.png"),plot = plot12, width=12, height=10, dpi=600, units="cm")

ggsave(filename = here::here(eda_figures_dir, "rawdata2.png"),plot = plot2, width=12, height=10, dpi=600, units="cm")

print(plot12)
print(plot2)

figure_2<-plot12
```

## Patients demographics
```{r summary-tbl}

tab1<-xdata %>% 
  distinct(ID,.keep_all = TRUE) %>%
 mutate(SEX=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA)) %>%
  select(ID, WT, AGE, SEX) %>%
  rename("Body Weigh, kg" = WT, "Age, y" = AGE, "Sex" = SEX) 
  
tab2<-xdata %>% 
  distinct(ID,.keep_all = TRUE) %>%
  pt_cont_long(cols = c("Body Weight, kg" = "WT", "Age, y" = "AGE" )) %>% 
  st_new()

tab3<-xdata %>% 
  distinct(ID,.keep_all = TRUE) %>%
 mutate(SEX=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA)) %>%
  pt_cat_long(cols = c("Sex" = "SEX")) %>% 
  st_new()

write.csv(tab1, file = here::here(eda_tables_dir, "icov.csv"))

tab1%>%kableExtra::kable()
tab2$data%>% kableExtra::kable()
tab3$data%>% kableExtra::kable()
```

# Stan

# M1: 2cmp disposition model + 1 comp abs

$$
\begin{aligned}
& \frac{dA}{dt} = - KA \cdot  A \\
& V_1 \cdot \frac{dC_1}{dt} =  KA \cdot  A - CL \cdot  C_1 - Q \cdot  C_1 + Q \cdot  C_2 \\
& V_2 \cdot \frac{dC_2}{dt} =  Q \cdot  C1 - Q \cdot  C_2
\end{aligned}
$$

where $C_1$ and $C_2$ denote sufentanil concentrations in plasma and peripheral compartment. $KA$ denotes sufentanil absorption rate constant. The statistical model has the following structure (hierarchical model)

$$ 
\begin{aligned}
& \log C_{Obs_{i,j}} \sim student\_t(\nu,f(P_{i},t_{i,j}),\sigma) \\
& \log P_{i} \sim \text{MVN}(\log \theta_P , \Omega) \\
\end{aligned}
$$

where $P_i=(CL_{i}, Q_{i}, V1_{i}, V2_{i}, KA_{i})$ is a vector of subject-specific parameters, $f(.)$ corresponds to the above ODE equations, $MVN$ is a multivariate normal distribution, $\theta_P$ is a vector of typical values of $P_i$. In turn, $\sigma$ is the scale and $\Omega$ is the scale matrix for the random effects related to the residual and unexplained between-subject variability. For convenience $\Omega$ was decomposed to:

$$
\Omega = diag(\omega) \cdot LL' \cdot diag(\omega) 
$$

where $\rho = LL'$ denotes correlation, $L$ is a lower triangular Cholesky factor for a correlation matrix and $\omega$ denotes standard deviation for between subject variability.

The priors were specified based on parameter estimates provided by our previous work [@Bartkowska-Sniatkowska2016-hm]
$$ 
\begin{aligned}
& \theta_{CL} \sim lognormal(log(45.3),0.25), \\
& \theta_{Q}  \sim lognormal(log(38.3),0.25), \\
& \theta_{V1} \sim lognormal(log(7.90),0.25), \\
& \theta_{V2} \sim lognormal(log(481),0.25), \\
& \theta_{KA} \sim lognormal(log(1),0.50), \\
& \nu \sim gamma(2,0.1),\\
& \omega_{P}\sim lognormal(log(0.4),0.25), \\
& \sigma \sim lognormal(log(0.2),0.25), \\
& L \sim  LKJ(5)
\end{aligned}
$$

LKJ(5) ensure that the density is uniform over correlation matrices of order 4 

```{r  model0, eval = FALSE}
mod0 <- new_model(file.path(model_dir, "0"), .model_type = "stan")
#open_standata_file(mod0)
#check_stan_model(mod0)
#mod0 <- mod0 %>% submit_model(.overwrite = TRUE) 
```

```{r  model1, eval = FALSE}
mod1  <- read_model(file.path(model_dir, "1"))
#open_standata_file(mod1)
#check_stan_model(mod1)
mod1_res <- mod1 %>% submit_model(.overwrite = TRUE) 
```
## Run stan
```{r load-stan-mod1}
model_name = "1"

model_figures_dir <- here::here(figures_dir, model_name)
model_tables_dir <- here::here(tables_dir,model_name)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

mod1  <- read_model(here::here(model_dir, model_name))
mod_to_plot <- read_fit_model(mod1)

xdata <- xdata %>%
    filter(OUT!=1, CMT!=22, CMT!=33) %>%
  mutate(TIME = if_else(infusion==0,timepostinf,TIMEh))

loo1 = mod_to_plot$loo()
```

## Parameters
```{r table-mod1, eval = TRUE}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat","omega", "sigma","nu","rho")

ptable <-plot_param_tables(mod_to_plot, pars)
ptable%>% knitr::kable()

writeLines(knitr::kable(ptable %>%
                          select(-mad,-ess_bulk,-ess_tail) %>%
                          filter(str_detect(parameter,"rho", negate = TRUE)), format = "latex"),  
           here::here(model_tables_dir, "parameters-table.tex"))

write.csv(ptable, file = here::here(model_tables_dir, "parameters-table.csv"))
```

## Trace plots
```{r trace-plots-mod1}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat","KAHat","omega", "sigma", "nu")

p1=bayesplot::mcmc_trace(mod_to_plot$draws(pars))
p2=bayesplot::mcmc_dens_overlay(mod_to_plot$draws(pars))

p1
p2

ggsave(filename = here::here(model_figures_dir, "trace-plots.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
ggsave(filename = here::here(model_figures_dir, "dense-plots.png"),plot = p2, width=12, height=10, dpi=600, units="cm")
```

## Individual and population predictions
```{r IPRED-PRED-mod1}
ppc1 <- pred_by_id_fun(mod_to_plot, xdata)
ppc1
ggsave(filename = here::here(model_figures_dir, "pred-by-id.png"),plot = ppc1, width=12, height=10, dpi=600, units="cm")

```

## VPC
```{r VPC-mod1}
vpc_plot<-vpc_fun(mod_to_plot, xdata)
vpc_plot
ggsave(filename = here::here(model_figures_dir, "vpc.png"),plot = vpc_plot, width=12, height=10, dpi=600, units="cm")
figure_4a<-vpc_plot
```

## GOF
```{r GOF-mod1, include=TRUE}
plot_gof <-gof_fun(mod_to_plot, xdata)
plot_gof
 
ggsave(filename = here::here(model_figures_dir, "gof.png"),plot = plot_gof, width=12, height=10, dpi=600, units="cm")
```

## Individual parameters vs. covariates
```{r covariets-mod1, include=TRUE}

etaM<-extract_etas_fun(mod_to_plot,xdata)

cont_cov = c("AGE//Age,y","WT//Body Weight, kg")
cat_cov = c("SEXF//Sex")

p1<-map(cont_cov, \(x) fun_cont_cov(x,etaM))
p2<-map(cat_cov, \(x) fun_cat_cov(x,etaM))

plots <- c(p1,p2)

plots

map(1:length(plots), \(x) ggsave(filename = here::here(model_figures_dir, 
                                 glue::glue("cov-plots-{x}.png")),
                                 plot = plots[[x]], 
                                 width=12, height=10, 
                                 dpi=600, units="cm"))
```

# M2: 2cmp disposition model + 1 comp abs. Wider prior distribution

The statistical model now allows for the between-study difference in PK parameters reflected by $\theta_{fr}$

$$ 
\begin{aligned}
& \log C_{Obs_{i,j}} \sim student\_t(\nu,f(P_{i},t_{i,j}),\sigma) \\
& \log P_{i} \sim \text{MVN}(\log (\theta_P \cdot \theta_{fr})  , \Omega) \\
\end{aligned}
$$
$fr$ is a form of a commensurate prior [@hobbs_commensurate_2012].

$$ 
\begin{aligned}
& \theta_{fr} \sim lognormal(log(1),0.25), \\
\end{aligned}
$$
```{r  model2, eval = FALSE}
#mod1  <- read_model(file.path(model_dir, "1"))
#mod2 <- copy_model_from(mod1, "2", "allow for the difference in pk parameters",.overwrite=T)

mod2  <- read_model(file.path(model_dir, "2"))
mod2_res <- mod2 %>% submit_model(.overwrite = TRUE) 
```

## Run stan
```{r load-stan-mod2}
model_name = "2"

model_figures_dir <- here::here(figures_dir, model_name)
model_tables_dir <- here::here(tables_dir,model_name)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

mod2  <- read_model(here::here(model_dir, model_name))
mod_to_plot <- read_fit_model(mod2)

xdata <- xdata %>%
    filter(OUT!=1, CMT!=22, CMT!=33) %>%
  mutate(TIME = if_else(infusion==0,timepostinf,TIMEh))
```

## Parameters
```{r table-mod2, eval = TRUE}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat", "fr", "omega", "sigma","nu","rho")

ptable <-plot_param_tables(mod_to_plot, pars)

ptable%>%
  knitr::kable()
writeLines(knitr::kable(ptable %>%
                          select(-mad,-ess_bulk,-ess_tail) %>%
                          filter(str_detect(parameter,"rho", negate = TRUE)), format = "latex"),  
           here::here(model_tables_dir, "parameters-table.tex"))
write.csv(ptable, file = here::here(model_tables_dir, "parameters-table.csv"))
```

## Parameters (figure)

```{r param2-mod2}
p1=bayesplot::mcmc_intervals(mod_to_plot$draws("fr"))
ggsave(filename = here::here(model_figures_dir, "fr-values.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
p1
```

## Trace plots
```{r trace-plots-mod2}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat","KAHat","omega", "sigma", "fr", "nu")

p1=bayesplot::mcmc_trace(mod_to_plot$draws(pars))
p2=bayesplot::mcmc_dens_overlay(mod_to_plot$draws(pars))

p1
p2

ggsave(filename = here::here(model_figures_dir, "trace-plots.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
ggsave(filename = here::here(model_figures_dir, "dense-plots.png"),plot = p2, width=12, height=10, dpi=600, units="cm")
```

## Individual and population predictions
```{r IPRED-PRED-mod2}
ppc1 <- pred_by_id_fun(mod_to_plot, xdata)
ppc1
ggsave(filename = here::here(model_figures_dir, "pred-by-id.png"),plot = ppc1, width=12, height=10, dpi=600, units="cm")
```

## VPC
```{r VPC-mod2}
vpc_plot<-vpc_fun(mod_to_plot, xdata)
vpc_plot

ggsave(filename = here::here(model_figures_dir, "vpc.png"),plot = vpc_plot, width=12, height=10, dpi=600, units="cm")
```

## GOF
```{r GOF-mod2, include=TRUE}
plot_gof <-gof_fun(mod_to_plot, xdata)
plot_gof
ggsave(filename = here::here(model_figures_dir, "gof.png"),plot = plot_gof, width=12, height=10, dpi=600, units="cm")
```
## Individual parameters vs. covariates

```{r covariets-mod2, include=TRUE}
etaM<-extract_etas_fun(mod_to_plot,xdata)

cont_cov = c("AGE//Age,y","WT//Body Weight, kg")
cat_cov = c("SEXF//Sex")

p1 <- map(cont_cov, \(x) fun_cont_cov(x,etaM))
p2 <- map(cat_cov, \(x) fun_cat_cov(x,etaM))

plots <- c(p1,p2)
plots
map(1:length(plots), \(x) ggsave(filename = here::here(model_figures_dir, 
                                 glue::glue("cov-plots-{x}.png")),
                                 plot = plots[[x]], 
                                 width=12, height=10, 
                                 dpi=600, units="cm"))
```

# M3: 2cmp model + 2cmp absorption

$$
\begin{aligned}
& \frac{dA1}{dt} = - KA \cdot  A1 - KA14 \cdot  A1 + KA41 \cdot  A4 \\
& \frac{dA4}{dt} =  KA14 \cdot  A1 - KA41 \cdot  A4 \\
& V_1 \cdot \frac{dC_1}{dt} =  KA \cdot  A1 - CL \cdot  C_1 - Q \cdot  C_1 + Q \cdot  C_2 \\
& V_2 \cdot \frac{dC_2}{dt} =  Q \cdot  C1 - Q \cdot  C_2
\end{aligned}
$$
$$ 
\begin{aligned}
& \theta_{KA} \sim lognormal(log(1),0.50), \\
& \theta_{KA14} \sim lognormal(log(4.85),0.50), \\
& \theta_{KA41} \sim lognormal(log(0.080),0.50), \\
\end{aligned}
$$

```{r  model3, eval = FALSE}
#mod1  <- read_model(file.path(model_dir, "1"))
#mod3 <- copy_model_from(mod1, "3", "absorption2",.overwrite=T)

mod3  <- read_model(file.path(model_dir, "3"))
mod3_res <- mod3 %>% submit_model(.overwrite = TRUE) 
```

## Run stan
```{r load-stan-mod3}
model_name = "3"

model_figures_dir <- here::here(figures_dir, model_name)
model_tables_dir <- here::here(tables_dir,model_name)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

mod2  <- read_model(here::here(model_dir, model_name))
mod_to_plot <- read_fit_model(mod2)

xdata <- xdata %>%
    filter(OUT!=1, CMT!=22, CMT!=33) %>%
  mutate(TIME = if_else(infusion==0,timepostinf,TIMEh))

loo3 = mod_to_plot$loo()
```

## Parameters
```{r table-mod3, eval = TRUE}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu","rho")

ptable <-plot_param_tables(mod_to_plot, pars)

ptable%>%
  knitr::kable()
writeLines(knitr::kable(ptable %>%
                          select(-mad,-ess_bulk,-ess_tail) %>%
                          filter(str_detect(parameter,"rho", negate = TRUE)), format = "latex"),  
           here::here(model_tables_dir, "parameters-table.tex"))
write.csv(ptable, file = here::here(model_tables_dir, "parameters-table.csv"))
```

### Half-lifes
```{r half-life}

thetaHat <- posterior::as_draws_df(mod_to_plot$draws(variables = c("thetaHat"))) %>% 
  mutate(
K10 = `thetaHat[5]`,
K14 = `thetaHat[6]`,
K41 = `thetaHat[7]`,
K20 = `thetaHat[1]`/`thetaHat[3]`,
K23 = `thetaHat[2]`/`thetaHat[3]`,
K32 = `thetaHat[2]`/`thetaHat[4]`,
beta_abs= 0.5*(K14+K41+K10-sqrt((K14+K41+K10)^2-4*K41*K10)),
alpha_abs = K41*K10/beta_abs,
beta_dis= 0.5*(K23+K32+K20-sqrt((K23+K32+K20)^2-4*K32*K20)),
alpha_dis = K32*K20/beta_dis,
thalf_beta_abs = 0.693/beta_abs,
thalf_alpha_abs = 0.693/alpha_abs,
thalf_beta_dis = 0.693/beta_dis,
thalf_alpha_dis = 0.693/alpha_dis) %>%
  summarise(mthalf_beta_abs = mean(thalf_beta_abs),
            sdthalf_beta_abs = sd(thalf_beta_abs),
mthalf_alpha_abs = mean(thalf_alpha_abs),
sdthalf_alpha_abs = sd(thalf_alpha_abs),
mthalf_beta_dis = mean(thalf_beta_dis),
sdthalf_beta_dis = sd(thalf_beta_dis),
mthalf_alpha_dis = mean(thalf_alpha_dis),
sdthalf_alpha_dis = sd(thalf_alpha_dis))

thetaHat
```

## Trace plots
```{r trace-plots-mod3}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu")

p1=bayesplot::mcmc_trace(mod_to_plot$draws(pars))
p2=bayesplot::mcmc_dens_overlay(mod_to_plot$draws(pars))

p1
p2

ggsave(filename = here::here(model_figures_dir, "trace-plots.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
ggsave(filename = here::here(model_figures_dir, "dense-plots.png"),plot = p2, width=12, height=10, dpi=600, units="cm")
```

## Pairs plots
```{r}
pars = c("CLHat", "QHat", "V1Hat", "V2Hat", "KAHat", "KA14Hat", "KA41Hat")

p1<-bayesplot::mcmc_pairs(mod_to_plot$draws(pars), pars, off_diag_args = list(size = 1, alpha = 0.5))

ggsave(filename = here::here(model_figures_dir, "dense-pairs.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
```

## Individual and population predictions
```{r IPRED-PRED-mod3}
ppc1 <- pred_by_id_fun(mod_to_plot, xdata)
ppc1
ggsave(filename = here::here(model_figures_dir, "pred-by-id.png"),plot = ppc1, width=12, height=10, dpi=600, units="cm")
figure_3<-ppc1
```

## VPC
```{r VPC-mod3}
vpc_plot<-vpc_fun(mod_to_plot, xdata)
vpc_plot

ggsave(filename = here::here(model_figures_dir, "vpc.png"),plot = vpc_plot, width=12, height=10, dpi=600, units="cm")
figure_4b<-vpc_plot
```

## GOF
```{r GOF-mod3, include=TRUE}
plot_gof <-gof_fun(mod_to_plot, xdata)
plot_gof
ggsave(filename = here::here(model_figures_dir, "gof.png"),plot = plot_gof, width=12, height=10, dpi=600, units="cm")
figure_5<-plot_gof
```

## Individual parameters vs. covariates
```{r covariets-mod3, include=TRUE}
etaM<-extract_etas_fun(mod_to_plot,xdata)

cont_cov = c("AGE//Age,y","WT//Body Weight, kg")
cat_cov = c("SEXF//Sex")

p1 <- map(cont_cov, \(x) fun_cont_cov(x,etaM))
p2 <- map(cat_cov, \(x) fun_cat_cov(x,etaM))

plots <- c(p1,p2)
plots
map(1:length(plots), \(x) ggsave(filename = here::here(model_figures_dir, 
                                 glue::glue("cov-plots-{x}.png")),
                                 plot = plots[[x]], 
                                 width=12, height=10, 
                                 dpi=600, units="cm"))
```

## Shrinkage
```{r}
etas <-  posterior::as_draws_df(mod_to_plot$draws("etaM"))%>%
  mutate(across(starts_with("eta"), ~log(.x)))
errors <-  posterior::as_draws_df(mod_to_plot$draws("errors"))

bbr.bayes::shrinkage(etas,"etaM",group_idx = 1, use_sd = TRUE)
bbr.bayes::shrinkage(errors,"errors", use_sd = TRUE)
```

# M3p: Prior predicitve check. 2cmp model + 2cmp absorption

```{r  model3a, eval = FALSE}
#mod3  <- read_model(file.path(model_dir, "3"))
#mod3a <- copy_model_from(mod3, "3a", "ppc",.overwrite=T)

mod3a  <- read_model(file.path(model_dir, "3a"))
mod3a_res <- mod3a %>% submit_model(.overwrite = TRUE) 
```

## Run stan
```{r load-stan-mod3a}
model_name = "3a"

model_figures_dir <- here::here(figures_dir, model_name)
model_tables_dir <- here::here(tables_dir,model_name)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

mod2  <- read_model(here::here(model_dir, model_name))
mod_to_plot <- read_fit_model(mod2)

xdata <- xdata %>%
    filter(OUT!=1, CMT!=22, CMT!=33) %>%
  mutate(TIME = if_else(infusion==0,timepostinf,TIMEh))
```

## Parameters
```{r table-mod3a, eval = TRUE}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu","rho")

ptable <-plot_param_tables(mod_to_plot, pars)

ptable%>%
  knitr::kable()

writeLines(knitr::kable(ptable %>%
                          select(-mad,-ess_bulk,-ess_tail) %>%
                          filter(str_detect(parameter,"rho", negate = TRUE)), format = "latex"),  
           here::here(model_tables_dir, "parameters-table.tex"))

write.csv(ptable, file = here::here(model_tables_dir, "parameters-table.csv"))
```

## Parameters (figure)

```{r param2-mod3a}
pars = c("CLHat", "QHat", "V1Hat", "V2Hat","KAHat", "KA14Hat", "KA41Hat")
p1=bayesplot::mcmc_intervals(mod_to_plot$draws(pars))
ggsave(filename = here::here(model_figures_dir, "fr-values.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
p1
```

## Trace plots
```{r trace-plots-mod3a}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu")

p1=bayesplot::mcmc_trace(mod_to_plot$draws(pars))
p2=bayesplot::mcmc_dens_overlay(mod_to_plot$draws(pars))

p1
p2

ggsave(filename = here::here(model_figures_dir, "trace-plots.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
ggsave(filename = here::here(model_figures_dir, "dense-plots.png"),plot = p2, width=12, height=10, dpi=600, units="cm")
```

## Individual and population predictions (Prior predictive check)
```{r IPRED-PRED-mod3a}
ppc1 <- pred_by_id_fun(mod_to_plot, xdata)
ppc1
ggsave(filename = here::here(model_figures_dir, "pred-by-id.png"),plot = ppc1, width=12, height=10, dpi=600, units="cm")

figure_1 <-ppc1
```

## VPC (Prior predictive check)
```{r VPC-mod3a}
vpc_plot<-vpc_fun(mod_to_plot, xdata)
vpc_plot

ggsave(filename = here::here(model_figures_dir, "vpc.png"),plot = vpc_plot, width=12, height=10, dpi=600, units="cm")
```


## Compare  M3p
### Parameters (figure)
```{r prior-posterior-mod3}
subdir = "3"

model_figures_dir <- here::here(figures_dir, subdir)
model_tables_dir <- here::here(tables_dir,subdir)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

modx  <- read_model(here::here(model_dir, "3"))
mod_to_plot1 <- read_fit_model(modx)
modx  <- read_model(here::here(model_dir, "3a"))
mod_to_plot2 <- read_fit_model(modx)

pars = c("CLHat", "QHat", "V1Hat", "V2Hat","KAHat", "KA14Hat", "KA41Hat")
p1=bayesplot::mcmc_intervals(mod_to_plot1$draws(pars))
p2=bayesplot::mcmc_intervals(mod_to_plot2$draws(pars))

p1_data = p1$plot$data%>%mutate(type = "posterior")
p2_data = p2$plot$data%>%mutate(type = "prior")

plot1= rbind(p1_data,p2_data)%>%
  ggplot(aes(y=type, x=m))+
  geom_point(size=2)+
  geom_linerange(aes(xmin = l, xmax = h), size=1)+
  geom_linerange(aes(xmin = ll, xmax = hh))+
  labs(x="",y="")+
  facet_wrap(~parameter, scales="free_x")
plot1
ggsave(filename = here::here(model_figures_dir, "prior-posterior-1.png"),plot = plot1, width=12, height=10, dpi=600, units="cm")

pars = c("omega", "sigma", "nu")
p1=bayesplot::mcmc_intervals(mod_to_plot1$draws(pars))
p2=bayesplot::mcmc_intervals(mod_to_plot2$draws(pars))

p1_data = p1$plot$data%>%mutate(type = "posterior")
p2_data = p2$plot$data%>%mutate(type = "prior")

plot2 = rbind(p1_data,p2_data)%>%
  ggplot(aes(y=type, x=m))+
  geom_point(size=2)+
  geom_linerange(aes(xmin = l, xmax = h), size=1)+
  geom_linerange(aes(xmin = ll, xmax = hh))+
  labs(x="",y="")+
  facet_wrap(~parameter, scales="free_x")
plot2
ggsave(filename = here::here(model_figures_dir, "prior-posterior-2.png"), plot = plot2, width=12, height=10, dpi=600, units="cm")

pars = c("rho")
p1=bayesplot::mcmc_intervals(mod_to_plot1$draws(pars))
p2=bayesplot::mcmc_intervals(mod_to_plot2$draws(pars))

p1_data = p1$plot$data%>%mutate(type = "posterior")
p2_data = p2$plot$data%>%mutate(type = "prior")

plot3 = rbind(p1_data,p2_data)%>%
  ggplot(aes(y=type, x=m))+
  geom_point(size=2)+
  geom_linerange(aes(xmin = l, xmax = h), size=1)+
  geom_linerange(aes(xmin = ll, xmax = hh))+
  labs(x="",y="")+
  facet_wrap(~parameter, scales="free_x")+
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")), 
        legend.text=element_text(size=6),
        legend.title =element_text(size=6))
plot3
ggsave(filename = here::here(model_figures_dir, "prior-posterior-3.png"), plot = plot3, width=12, height=10, dpi=600, units="cm")

```

# M4: 3 comp. model Different Priors (Based on https://pubmed.ncbi.nlm.nih.gov/8533912/)
```{r  model4, eval = FALSE}
mod4  <- read_model(file.path(model_dir, "4"))
mod4_res <- mod4 %>% submit_model(.overwrite = TRUE) 
```

## Run stan
```{r load-stan-mod4}
model_name = "4"

model_figures_dir <- here::here(figures_dir, model_name)
model_tables_dir <- here::here(tables_dir,model_name)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

mod2  <- read_model(here::here(model_dir, model_name))
mod_to_plot <- read_fit_model(mod2)

xdata <- xdata %>%
    filter(OUT!=1, CMT!=22, CMT!=33) %>%
  mutate(TIME = if_else(infusion==0,timepostinf,TIMEh))
```

## Parameters
```{r table-mod4, eval = F}
pars = c("lp__", "CLHat", "Q1Hat", "Q2Hat", "V1Hat", "V2Hat", "V3Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu","rho")

ptable <-plot_param_tables(mod_to_plot, pars)

ptable%>% knitr::kable()

writeLines(knitr::kable(ptable %>%
                          select(-mad,-ess_bulk,-ess_tail) %>%
                          filter(str_detect(parameter,"rho", negate = TRUE)), format = "latex"),  
           here::here(model_tables_dir, "parameters-table.tex"))

write.csv(ptable, file = here::here(model_tables_dir, "parameters-table.csv"))
```

## Trace plots
```{r trace-plots-mod4}
pars = c("lp__", "CLHat", "Q1Hat", "Q2Hat", "V1Hat", "V2Hat", "V3Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu")

p1=bayesplot::mcmc_trace(mod_to_plot$draws(pars))
p2=bayesplot::mcmc_dens_overlay(mod_to_plot$draws(pars))

p1
p2

ggsave(filename = here::here(model_figures_dir, "trace-plots.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
ggsave(filename = here::here(model_figures_dir, "dense-plots.png"),plot = p2, width=12, height=10, dpi=600, units="cm")
```

# M4p: Prior predicitve check.  Different Priors (Based on https://pubmed.ncbi.nlm.nih.gov/8533912/)
```{r  model4a, eval = FALSE}
mod4a  <- read_model(file.path(model_dir, "4a"))
# mod4a <- copy_model_from(mod4, "4a", "prior change",.overwrite=T)
mod4a_res <- mod4a %>% submit_model(.overwrite = TRUE) 
```

## Run stan
```{r load-stan-mod4a}
model_name = "4a"

model_figures_dir <- here::here(figures_dir, model_name)
model_tables_dir <- here::here(tables_dir,model_name)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

mod2  <- read_model(here::here(model_dir, model_name))
mod_to_plot <- read_fit_model(mod2)

xdata <- xdata %>%
    filter(OUT!=1, CMT!=22, CMT!=33) %>%
  mutate(TIME = if_else(infusion==0,timepostinf,TIMEh))
```

## Parameters
```{r table-mod4a, eval = TRUE}
pars = c("lp__", "CLHat", "Q1Hat", "Q2Hat", "V1Hat", "V2Hat", "V3Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu","rho")

ptable <-plot_param_tables(mod_to_plot, pars)

writeLines(knitr::kable(ptable %>%
                          select(-mad,-ess_bulk,-ess_tail) %>%
                          filter(str_detect(parameter,"rho", negate = TRUE)), format = "latex"),  
           here::here(model_tables_dir, "parameters-table.tex"))

write.csv(ptable, file = here::here(model_tables_dir, "parameters-table.csv"))
```


## Trace plots
```{r trace-plots-mod4a}
pars = c("lp__", "CLHat", "Q1Hat", "Q2Hat", "V1Hat", "V2Hat", "V3Hat",
         "KAHat", "KA14Hat", "KA41Hat", "omega", "sigma","nu")

p1=bayesplot::mcmc_trace(mod_to_plot$draws(pars))
p2=bayesplot::mcmc_dens_overlay(mod_to_plot$draws(pars))

p1
p2

ggsave(filename = here::here(model_figures_dir, "trace-plots.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
ggsave(filename = here::here(model_figures_dir, "dense-plots.png"),plot = p2, width=12, height=10, dpi=600, units="cm")
```

## Individual and population predictions (Prior predictive check)
```{r IPRED-PRED-mod4a}
ppc1 <- pred_by_id_fun(mod_to_plot, xdata)
ppc1
ggsave(filename = here::here(model_figures_dir, "pred-by-id.png"),plot = ppc1, width=12, height=10, dpi=600, units="cm")
```

## VPC (Prior predictive check)
```{r VPC-mod4a}
vpc_plot<-vpc_fun(mod_to_plot, xdata)
vpc_plot

ggsave(filename = here::here(model_figures_dir, "vpc.png"),plot = vpc_plot, width=12, height=10, dpi=600, units="cm")
```

# M5: 2cmp model + 2cmp absorption + KA41~SEX

$$
\begin{aligned}
& \frac{dA1}{dt} = - KA \cdot  A1 - KA14 \cdot  A1 + KA41 \cdot  A4 \\
& \frac{dA4}{dt} =  KA14 \cdot  A1 - KA41 \cdot  A4 \\
& V_1 \cdot \frac{dC_1}{dt} =  KA \cdot  A1 - CL \cdot  C_1 - Q \cdot  C_1 + Q \cdot  C_2 \\
& V_2 \cdot \frac{dC_2}{dt} =  Q \cdot  C1 - Q \cdot  C_2
\end{aligned}
$$
$$ 
\begin{aligned}
& \theta_{KA} \sim lognormal(log(1),0.50), \\
& \theta_{KA14} \sim lognormal(log(4.85),0.50), \\
& \theta_{KA41} \sim lognormal(log(0.080),0.50), \\
& \theta_{LOGKA41SEX} \sim normal(0,0.25), \\
\end{aligned}
$$

```{r  model5, eval = FALSE}
mod5  <- read_model(file.path(model_dir, "5"))
mod5_res <- mod5 %>% submit_model(.overwrite = TRUE) 
```

## Run stan
```{r load-stan-mod5}
model_name = "5"

model_figures_dir <- here::here(figures_dir, model_name)
model_tables_dir <- here::here(tables_dir,model_name)
dir.create(model_figures_dir, recursive = T)
dir.create(model_tables_dir, recursive = T)

mod2  <- read_model(here::here(model_dir, model_name))
mod_to_plot <- read_fit_model(mod2)

xdata <- xdata %>%
    filter(OUT!=1, CMT!=22, CMT!=33) %>%
  mutate(TIME = if_else(infusion==0,timepostinf,TIMEh))

loo5 = mod_to_plot$loo()
```

## Parameters
```{r table-mod5, eval = TRUE}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat", "KA14Hat", "KA41Hat", "logKA14SEXHat", "omega", "sigma","nu","rho")

ptable <-plot_param_tables(mod_to_plot, pars)

ptable%>% knitr::kable()

writeLines(knitr::kable(ptable %>%
                          select(-mad,-ess_bulk,-ess_tail) %>%
                          filter(str_detect(parameter,"rho", negate = TRUE)), format = "latex"),  
           here::here(model_tables_dir, "parameters-table.tex"))

write.csv(ptable, file = here::here(model_tables_dir, "parameters-table.csv"))
```


## Trace plots
```{r trace-plots-mod5}
pars = c("lp__", "CLHat", "QHat", "V1Hat", "V2Hat",
         "KAHat", "KA14Hat", "KA41Hat", "logKA14SEXHat", "omega", "sigma","nu")

p1=bayesplot::mcmc_trace(mod_to_plot$draws(pars))
p2=bayesplot::mcmc_dens_overlay(mod_to_plot$draws(pars))

p1
p2

ggsave(filename = here::here(model_figures_dir, "trace-plots.png"),plot = p1, width=12, height=10, dpi=600, units="cm")
ggsave(filename = here::here(model_figures_dir, "dense-plots.png"),plot = p2, width=12, height=10, dpi=600, units="cm")
```

## Individual and population predictions
```{r IPRED-PRED-mod5}
ppc1 <- pred_by_id_fun(mod_to_plot, xdata)
ppc1
ggsave(filename = here::here(model_figures_dir, "pred-by-id.png"),plot = ppc1, width=12, height=10, dpi=600, units="cm")
```

## VPC
```{r VPC-mod5}
vpc_plot<-vpc_fun(mod_to_plot, xdata)
vpc_plot

ggsave(filename = here::here(model_figures_dir, "vpc.png"),plot = vpc_plot, width=12, height=10, dpi=600, units="cm")
```

## GOF
```{r GOF-mod5, include=TRUE}
plot_gof <-gof_fun(mod_to_plot, xdata)
plot_gof
ggsave(filename = here::here(model_figures_dir, "gof.png"),plot = plot_gof, width=12, height=10, dpi=600, units="cm")
```

## Individual parameters vs. covariates
```{r covariets-mod5, include=TRUE}
etaM<-extract_etas_fun(mod_to_plot,xdata)

cont_cov = c("AGE//Age,y","WT//Body Weight, kg")
cat_cov = c("SEXF//Sex")

p1 <- map(cont_cov, \(x) fun_cont_cov(x,etaM))
p2 <- map(cat_cov, \(x) fun_cat_cov(x,etaM))

plots <- c(p1,p2)
plots
map(1:length(plots), \(x) ggsave(filename = here::here(model_figures_dir, 
                                 glue::glue("cov-plots-{x}.png")),
                                 plot = plots[[x]], 
                                 width=12, height=10, 
                                 dpi=600, units="cm"))
```

# Compare models 
## Based on generated-quantities
```{r compare-models-log-lik - gq, eval=FALSE}
# mod5  <- read_model(file.path(model_dir, "5"))
# mod5_gq <- copy_model_as_stan_gq(mod5, .overwrite = TRUE)
mod1_gq  <- read_model(file.path(model_dir, "1_gq"))
mod1_gq <- submit_model(mod1_gq,.overwrite = TRUE)
mod3_gq  <- read_model(file.path(model_dir, "3_gq"))
mod3_gq <- submit_model(mod3_gq,.overwrite = TRUE)
mod5_gq  <- read_model(file.path(model_dir, "5_gq"))
mod5_gq <- submit_model(mod5_gq,.overwrite = TRUE)

files <- list.files(path = here::here(mod1_gq$absolute_model_path,"1_gq-output"),
                    pattern = "\\.csv$", 
                    ignore.case = TRUE, full.names=TRUE)

temp <- cmdstanr::read_cmdstan_csv(files)
ll1 <- as_draws_array(temp$generated_quantities)

files <- list.files(path = here::here(mod3_gq$absolute_model_path,"3_gq-output"),
                    pattern = "\\.csv$", 
                    ignore.case = TRUE, full.names=TRUE)

temp <- cmdstanr::read_cmdstan_csv(files)
ll3 <- as_draws_array(temp$generated_quantities)

files <- list.files(path = here::here(mod5_gq$absolute_model_path,"5_gq-output"),
                    pattern = "\\.csv$", 
                    ignore.case = TRUE, full.names=TRUE)

temp <- cmdstanr::read_cmdstan_csv(files)
ll5 <- as_draws_array(temp$generated_quantities)

loo1 <- loo(ll1) 
loo3 <- loo(ll3)  
loo5 <- loo(ll5)
```

## Direct method
```{r cmdstanr-loo, model-comparison}
comp <- loo_compare(list("2cmpdisp-1compabs" = loo1, 
                         "2cmpdisp-2cmpabs"=loo3,
                         "2cmpdisp-2cmpabs-cov"=loo5))
print(comp, digits = 2)
```
## Moment matched 

```{r, eval=FALSE}
mod1 <- read_fit_model(read_model(here::here(model_dir, "1")))
mod3 <- read_fit_model(read_model(here::here(model_dir, "3")))
mod5 <- read_fit_model(read_model(here::here(model_dir, "5")))

loo1 = mod1$loo(r_eff = 1,moment_match = T, cores = getOption("mc.cores", 10))
loo3 = mod3$loo(r_eff = 1,moment_match = T, cores = getOption("mc.cores", 10))
loo5 = mod5$loo(r_eff = 1,moment_match = T, cores = getOption("mc.cores", 10))

comp <- loo_compare(list("2cmpdisp-1compabs" = loo1, 
                         "2cmpdisp-2cmpabs"=loo3,
                         "2cmpdisp-2cmpabs-cov"=loo5))

print(comp, digits = 2)

stacking_wts <- stacking_weights(cbind(loo1$pointwise[, "elpd_loo"], 
                                       loo3$pointwise[, "elpd_loo"],
                                       loo5$pointwise[, "elpd_loo"]))

stacking_wts
```
# Manuscript
```{r manuscript-figures}
manuscript_figures_dir <- here::here(figures_dir, "manuscript")
dir.create(manuscript_figures_dir, recursive = T)

inf_labs <- c("TRUE" = "During infusion",
  "FALSE" = "Post infusion")

figure_4a <- figure_4a +
  facet_manual(~infusion, design = "BA",
               labeller = labeller(infusion = inf_labs),
                scales = "free_x")+
  scale_x_facet(infusion == TRUE, limits = c(0, 60))

figure_4b <- figure_4b +
  facet_manual(~infusion, design = "BA", 
               labeller = labeller(infusion = inf_labs),
                scales = "free_x") +
  scale_x_facet(infusion == TRUE, limits = c(0, 60))

figure_1 <- figure_1 + theme(legend.position="none")
figure_4 <- figure_4a/figure_4b+
  plot_layout(guides = "collect")+
  plot_annotation(tag_levels = 'A')&
                  theme(plot.title = element_text(size = 8),
                                axis.title = element_text(size = 8),
                                axis.text  = element_text(size = 6))

ggsave(filename = here::here(manuscript_figures_dir, "figure1.png"),plot = figure_1, width=16, height=12, dpi=600, units="cm")
ggsave(filename = here::here(manuscript_figures_dir, "figure2.png"),plot = figure_2, width=16, height=12, dpi=600, units="cm")
ggsave(filename = here::here(manuscript_figures_dir, "figure3.png"),plot = figure_3, width=16, height=12, dpi=600, units="cm")
ggsave(filename = here::here(manuscript_figures_dir, "figure4.png"),plot = figure_4, width=16, height=18, dpi=600, units="cm")
ggsave(filename = here::here(manuscript_figures_dir, "figure5.png"),plot = figure_5, width=16, height=12, dpi=600, units="cm")

figure_1
figure_2
figure_3
figure_4
figure_5
```

# References {.unnumbered}

::: {#refs}
:::

# Licenses {.unnumbered}

-   Code & copy; 2025, Paweł Wiczling, licensed under BSD-3.
-   Text & copy; 2025, Paweł Wiczling, licensed under CC-BY-NC 4.0.

# Original Computing Environment {.unnumbered}

```{r sessionInfo}
sessionInfo()
```