---
title: "Pharmacokinetics of sufentanil after epidural administration"
author:   
  - Pawel Wiczling
  - Agnieszka Bienert
  - Paulina Okuńska
  - Agnieszka Borsuk-de Moor
  - Justyna Ber
date: today
date-format: long
format:
  html:
    toc: true
    code-fold: true
execute:
  warning: false
---

# Introduction

Pharmacokinetics of sufentanil after epidural administration:

```{r lib, message=FALSE}

library(pracma)
library(bbr)
library(dplyr)
library(ggplot2)
library(patchwork)
library(mrgsolve)
library(vpc)
library(pmplots)
library(scales)
library(data.table)
library(tidyverse)
library(glue)
library(whisker)
library(here)

library(pmtables)

# library(mrgmisc)
source("functions/resampling_functions.R") # from mrgmisc
```

Settings:

```{r settings}

data_dir <- "../data/derived" 
model_dir <- "../model/nonmem/basic"  
figure_dir <- "../deliv/figures" 

# user specific settings
options(bbr.bbi_exe_path = "C:/Users/pawel/AppData/Roaming/bbi/bbi.exe")

bbi_init(.dir = model_dir,            # the directory to create the bbi.yaml in
         .nonmem_dir = "C:/",         # location of NONMEM installation
         .nonmem_version = "nm74g64",  # default NONMEM version to use
.bbi_args = list(
     mpi_exec_path ="C:/nm74g64/run/psexec",
      parafile = "C:/nm74g64/run/fpiwini8.pnm",
      parallel = TRUE,
      threads = 4
    )
)
```

# Data

Load data:

```{r load-data}
xdata <- read.csv(paste0(data_dir, "/", "nonmem_data_v02.csv"), na.strings='.')
```

## Plot raw data:

```{r plotrawdata}
#' Some plots
#' 

xdata$outliers = xdata$OUT;
xdata$infusion = xdata$TIMEh<xdata$TINFS;
xdata$timepostinf = xdata$TIMEh-xdata$TINFS;

plot1<-ggplot(data = subset(xdata, EVID == 0 & outliers==0 & infusion==1), aes(x = TIMEh, y = DV, group = ID)) + 
  geom_point() + 
  geom_line() + 
  geom_point(data = subset(xdata, EVID == 0 & outliers==1 & infusion==1), aes(x = TIMEh, y = DV, group = ID),colour = "red") + 
scale_y_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+
  ylab("Sufentanil concentrations, pg/ml") +
  xlab("Time after infusion start, h") + 
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")), 
        legend.text=element_text(size=6),
        legend.title =element_text(size=6))

plot2<-ggplot(data = subset(xdata, EVID == 0 & outliers==0 & infusion==0), aes(x = timepostinf, y = DV, group = ID)) + 
  geom_point() + 
  geom_line() + 
  geom_point(data = subset(xdata, EVID == 0 & outliers==1 & infusion==0), aes(x = timepostinf, y = DV, group = ID),colour = "red") + 
scale_y_continuous(limits = c(0.1, 100),
                   trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+
 ylab(element_blank()) +
  xlab("Time after infusion end, h")+
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")), 
        legend.text=element_text(size=6),
        legend.title =element_text(size=6))

plot12 <-plot1+plot2

ggsave(filename = paste0(figure_dir, "/EDA/", "rawdata1.png"),plot = plot12, width=12, height=10, dpi=600, units="cm")


plot2<-ggplot(data = subset(xdata, EVID==0 & outliers==0), aes(x = TIMEh, y = DV, color = factor(ID)),shape=21) + 
  geom_point() +
  geom_line()+ 
scale_y_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+
  ylab("Sufentanil concentrations, pg/ml") +
  xlab("Time after infusion start, days") + 
  labs(color = "ID")+
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")), 
        legend.text=element_text(size=6),
        legend.title =element_text(size=6)) + 
  geom_segment(aes(x = 0, y = 100, xend = TINFS, yend = 100))+
  facet_wrap(.~factor(ID),nrow = 3)+
  theme(legend.position="none")


ggsave(filename = paste0(figure_dir, "/EDA/", "rawdata2.png"),plot = plot2, width=12, height=10, dpi=600, units="cm")


print(plot12)

cat("by individual")
print(plot2)

```

## Patients demographics

```{r summary-tbl}
xdata %>% 
  distinct(ID,.keep_all = TRUE) %>%
 mutate(SEX=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA)) %>%
  select(ID, WT, AGE, SEX) %>%
  rename("Body Weigh, kg" = WT, "Age, y" = AGE, "Sex" = SEX) %>%
  kableExtra::kable()
```

# Run NONMEM

Define few functions used later to visualize results:

```{r functions}
#' Functions


fig_model_fits_fun <- function(df){
  ggplot(data = subset(df, EVID==0), aes(x = TIME, y = DV)) + 
  geom_point(size=1) + 
  geom_line(data = subset(df,EVID!=1) , aes(x = TIME, y = IPRED), linetype=1) +
  geom_line(data = subset(df,EVID!=1) , aes(x = TIME, y = PRED), linetype=2) + 
  scale_y_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+
  ylab("Sufentanil concentrations, pg/ml") +
  xlab("Time, h") + 
  theme(axis.text.x = element_text(size=6),
        axis.text.y = element_text(size=6),
        axis.text = element_text(size=10),
        axis.title=element_text(size=10),
        strip.text.x = element_text(size = 6,margin = margin(0,0,0,0, "cm")),
        legend.text=element_text(size=6),
        legend.title =element_text(size=6))+
  facet_wrap(.~ID,nrow = 3)
}

fig_gof_fun <- function(df){
  
p1<-ggplot(subset(df,MDV==0),aes(x=IPRED,y=DV))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, linetype=2, color="gray")+
  labs( x="IPRED", y="DV")+ 
  scale_y_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+ 
  scale_x_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))

p2<-ggplot(subset(df,MDV==0),aes(x=PRED,y=DV))+
  geom_point()+
  geom_abline(intercept = 0, slope =1, linetype=2, color="gray")+
  labs( x="PRED", y="DV")+ 
  scale_y_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))+ 
  scale_x_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))

p3<-ggplot(subset(df,MDV==0),aes(x=TIME,y=CWRES))+
  geom_point()+
  geom_hline(yintercept = 0, linetype=2, color="gray") + 
  labs( x="Time (h)", y="CWRES")

p4<-ggplot(subset(df,MDV==0),aes(x=PRED,y=CWRES))+
  geom_point()+
  geom_hline(yintercept = 0, linetype=2, color="gray")+
  labs( x="PRED", y="CWRES")+ 
  scale_x_continuous(limits = c(0.1, 100),
                      trans='log10',
                      breaks=trans_breaks('log10', function(x) 10^x, n=4),
                      labels=trans_format('log10', math_format(10^.x)))

fig_gof<-(p1+p2)/(p3+p4)

return(fig_gof)
}

```

Model 1. Classical 2 cmp. model, 1-st order absorption.

```{r model1, eval = FALSE}
mod1 <- new_model(file.path(model_dir, 1),  .overwrite = TRUE)
submit_model(mod1, .mode = "local")
mod1 <- mod1 %>% 
  add_tags("2 cmp dispos. model, 1-st order abs.")%>% 
  add_tags("etas estiamted for CL/F") 
#mod1 <- mod1 %>% add_notes(" ")
```

Model 2. 2 cmp dispos. model (fixed), 1-st order abs., F estimated.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/26105145/>:
VC = 7.90 l, VT = 481 L, Cl = 45.3 L/h, and Q = 38.3 L/h

```{r model2, eval = FALSE}
mod2 <- new_model(file.path(model_dir, 2),  .overwrite = TRUE)
submit_model(mod2, .mode = "local")
mod2 <- mod2 %>% 
  add_tags("2 cmp dispos. model (fixed), 1-st order abs., F estimated")%>% 
  add_tags("etas estiamted for CL/F")
#mod2 <- mod2 %>% add_notes(" ")
```

Model 3. 2 cmp dispos. model (fixed), 1-st order 2-cmp abs., F=1.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/26105145/>:
VC = 7.90 l, VT = 481 L, Cl = 45.3 L/h, and Q = 38.3 L/h

```{r model3, eval = FALSE}
mod3 <- new_model(file.path(model_dir, 3),  .overwrite = TRUE)
submit_model(mod3, .mode = "local")
mod3 <- mod3 %>% 
  add_tags("2 cmp dispos. model (fixed), 1-st order 2-cmp abs., F=1")%>% 
  add_tags("etas estiamted for CL/F")
#mod3 <- mod3 %>% add_notes(" ")
```

Model 4. 2 cmp dispos. model (fixed), 1-st order 2-cmp abs., F estimated.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/26105145/>:
VC = 7.90 l, VT = 481 L, Cl = 45.3 L/h, and Q = 38.3 L/h


```{r model4, eval = FALSE}
mod4 <- new_model(file.path(model_dir, 4),  .overwrite = TRUE)
submit_model(mod4, .mode = "local")
mod4 <- mod4 %>% 
  add_tags("2 cmp dispos. model (fixed), 1-st order 2-cmp abs., F estimated")%>% 
  add_tags("etas estiamted for CL/F")
#mod4 <- mod4 %>% add_notes(" ")

```

Model 5. 3 cmp dispos. model (fixed), 1-st order abs., F estimated.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/8533912/>:
VC = 14.6, VP1 = 66, VP2 = 608, Cl = 52.8 L/h, and Q = 102 L/h i 40.8 L/h

```{r model5, eval = FALSE}

mod5 <- new_model(file.path(model_dir, 5),  .overwrite = TRUE)
submit_model(mod5, .mode = "local")
mod5 <- mod5 %>% 
  add_tags("3 cmp dispos. model (fixed), 1-st order abs., F estimated")%>% 
  add_tags("etas estiamted for CL/F")
#mod5 <- mod5 %>% add_notes(" ")

```

# Compare models:

```{r compare}
log_df <- run_log(model_dir)
log_df%>%
  select(-c(absolute_model_path,yaml_md5,bbi_args,based_on, star,model_type, description))%>%
  kableExtra::kable()
```

```{r ofv-summary}
summary_log(model_dir, .include = 1:5) %>%
  select(run, ofv, condition_number, any_heuristics) %>% 
  knitr::kable()
```

# Visualise key modeling steps

## Model 1

2 cmp dispos. model, 1-st order abs., etas estiamted for CL/F

```{r select-model1}
mod_to_plot <- read_model(file.path(model_dir, 1))
join_df <- nm_join(mod_to_plot) 

```

### Model summary

```{r mod1-summary}
 label_df <- mod_to_plot %>% 
  param_labels() %>% 
  apply_indices() 

param_df <- mod_to_plot %>% 
  model_summary() %>% 
  param_estimates()

report_df <- inner_join(
  label_df %>% select(-param_type),
  param_df %>% select(parameter_names, estimate, stderr, fixed),
  by = "parameter_names") %>%
  mutate(estimate=round(estimate, 3)) %>%
  mutate(stderr= case_when(
             stderr == 1.00e+10 ~ NA,
             .default = stderr)) %>%
  mutate(stderr=round(stderr, 3)) 

report_df%>% knitr::kable()
```

### Plot model fits


```{r model1-fits}
# Individual and population fits
fig_model_fits<- fig_model_fits_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "model_fits" , ".png"),
         plot=fig_model_fits, width=12, height=10, dpi=600, units="cm")

print(fig_model_fits)

```

### Plot GOF fits

```{r model1-gof}

fig_gof<-fig_gof_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" , "gof" , ".png"),
      plot=fig_gof, width=12, height=10, dpi=600, units="cm")

print(fig_gof) 

```

### Covariate relationships

```{r model1-cov}

idata <- distinct(join_df,ID,.keep_all = TRUE) 

idata<-idata %>%
 mutate(SEXC=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA))

etas <- c("ETA1//Eta for CL",
          "ETA2//Eta for V1",
          "ETA3//Eta for Q",
          "ETA4//Eta for V2",
          "ETA5//Eta for KA")

p_cat<-eta_cat(idata, c("SEXC//Sex"), etas)
p_cont1<-eta_cont(idata, c("AGE//Age, y"), etas)
p_cont2<-eta_cont(idata, c("WT//Weight, kg"), etas)
# cov_sex<-(p_cat[[1]]+p_cat[[2]])/(p_cat[[3]]+p_cat[[4]])/(p_cat[[5]]+plot_spacer())
# cov_age<-(p_cont1[[1]]+p_cont1[[2]])/(p_cont1[[3]]+p_cont1[[4]])/(p_cont1[[5]]+plot_spacer())
# cov_wt <-(p_cont2[[1]]+p_cont2[[2]])/(p_cont2[[3]]+p_cont2[[4]])/(p_cont2[[5]]+plot_spacer())

cov_sex<-p_cat[[1]]
cov_age<-p_cont1[[1]]
cov_wt <-p_cont2[[1]]

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_sex" , ".png"),
         plot=cov_sex, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_age" , ".png"),
         plot=cov_age, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_wt" , ".png"),
         plot=cov_wt, width=12, height=10, dpi=600, units="cm")

print(cov_sex)
print(cov_age)
print(cov_wt)
```

## Model 2

2 cmp dispos. model (fixed), 1-st order abs., F estimated, etas estiamted for CL/F.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/26105145/>:
VC = 7.90 l, VT = 481 L, Cl = 45.3 L/h, and Q = 38.3 L/h

```{r select-model2}
mod_to_plot <- read_model(file.path(model_dir, 2))
join_df <- nm_join(mod_to_plot) 

```

### Model summary

```{r mod2-summary}
 label_df <- mod_to_plot %>% 
  param_labels() %>% 
  apply_indices() 

param_df <- mod_to_plot %>% 
  model_summary() %>% 
  param_estimates()

report_df <- inner_join(
  label_df %>% select(-param_type),
  param_df %>% select(parameter_names, estimate, stderr, fixed),
  by = "parameter_names") %>%
  mutate(estimate=round(estimate, 3)) %>%
  mutate(stderr= case_when(
             stderr == 1.00e+10 ~ NA,
             .default = stderr)) %>%
  mutate(stderr=round(stderr, 3)) 

report_df%>% knitr::kable()
```

### Plot model fits

Model predictions:

```{r model2-fits}
# Individual and population fits
fig_model_fits<- fig_model_fits_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "model_fits" , ".png"),
         plot=fig_model_fits, width=12, height=10, dpi=600, units="cm")

print(fig_model_fits)

```

### Plot GOF fits

```{r model2-gof}

fig_gof<-fig_gof_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" , "gof" , ".png"),
      plot=fig_gof, width=12, height=10, dpi=600, units="cm")

print(fig_gof) 

```

### Covariate relationships

```{r model2-cov}

idata <- distinct(join_df,ID,.keep_all = TRUE) 

idata<-idata %>%
 mutate(SEXC=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA))

etas <- c("ETA1//Eta for CL",
          "ETA2//Eta for V1",
          "ETA3//Eta for Q",
          "ETA4//Eta for V2",
          "ETA5//Eta for KA")

p_cat<-eta_cat(idata, c("SEXC//Sex"), etas)
p_cont1<-eta_cont(idata, c("AGE//Age, y"), etas)
p_cont2<-eta_cont(idata, c("WT//Weight, kg"), etas)
# cov_sex<-(p_cat[[1]]+p_cat[[2]])/(p_cat[[3]]+p_cat[[4]])/(p_cat[[5]]+plot_spacer())
# cov_age<-(p_cont1[[1]]+p_cont1[[2]])/(p_cont1[[3]]+p_cont1[[4]])/(p_cont1[[5]]+plot_spacer())
# cov_wt <-(p_cont2[[1]]+p_cont2[[2]])/(p_cont2[[3]]+p_cont2[[4]])/(p_cont2[[5]]+plot_spacer())

cov_sex<-p_cat[[1]]
cov_age<-p_cont1[[1]]
cov_wt <-p_cont2[[1]]

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_sex" , ".png"),
         plot=cov_sex, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_age" , ".png"),
         plot=cov_age, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_wt" , ".png"),
         plot=cov_wt, width=12, height=10, dpi=600, units="cm")

print(cov_sex)
print(cov_age)
print(cov_wt)
```

## Model 3

2 cmp dispos. model (fixed), 1-st order 2-cmp abs., F=1, etas estiamted for CL/F.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/26105145/>:
VC = 7.90 l, VT = 481 L, Cl = 45.3 L/h, and Q = 38.3 L/h
```{r select-model3}
mod_to_plot <- read_model(file.path(model_dir, 3))
join_df <- nm_join(mod_to_plot) 

```

### Model summary

```{r mod3-summary}
 label_df <- mod_to_plot %>% 
  param_labels() %>% 
  apply_indices() 

param_df <- mod_to_plot %>% 
  model_summary() %>% 
  param_estimates()

report_df <- inner_join(
  label_df %>% select(-param_type),
  param_df %>% select(parameter_names, estimate, stderr, fixed),
  by = "parameter_names") %>%
  mutate(estimate=round(estimate, 3)) %>%
  mutate(stderr= case_when(
             stderr == 1.00e+10 ~ NA,
             .default = stderr)) %>%
  mutate(stderr=round(stderr, 3)) 

report_df%>% knitr::kable()
```

### Plot model fits

Model predictions:

```{r model3-fits}
# Individual and population fits
fig_model_fits<- fig_model_fits_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "model_fits" , ".png"),
         plot=fig_model_fits, width=12, height=10, dpi=600, units="cm")

print(fig_model_fits)

```

### Plot GOF fits

```{r model3-gof}

fig_gof<-fig_gof_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" , "gof" , ".png"),
      plot=fig_gof, width=12, height=10, dpi=600, units="cm")

print(fig_gof) 

```

### Covariate relationships

```{r model3-cov}

idata <- distinct(join_df,ID,.keep_all = TRUE) 

idata<-idata %>%
 mutate(SEXC=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA))

etas <- c("ETA1//Eta for CL",
          "ETA2//Eta for V1",
          "ETA3//Eta for Q",
          "ETA4//Eta for V2",
          "ETA5//Eta for KA")

p_cat<-eta_cat(idata, c("SEXC//Sex"), etas)
p_cont1<-eta_cont(idata, c("AGE//Age, y"), etas)
p_cont2<-eta_cont(idata, c("WT//Weight, kg"), etas)
# cov_sex<-(p_cat[[1]]+p_cat[[2]])/(p_cat[[3]]+p_cat[[4]])/(p_cat[[5]]+plot_spacer())
# cov_age<-(p_cont1[[1]]+p_cont1[[2]])/(p_cont1[[3]]+p_cont1[[4]])/(p_cont1[[5]]+plot_spacer())
# cov_wt <-(p_cont2[[1]]+p_cont2[[2]])/(p_cont2[[3]]+p_cont2[[4]])/(p_cont2[[5]]+plot_spacer())

cov_sex<-p_cat[[1]]
cov_age<-p_cont1[[1]]
cov_wt <-p_cont2[[1]]

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_sex" , ".png"),
         plot=cov_sex, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_age" , ".png"),
         plot=cov_age, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_wt" , ".png"),
         plot=cov_wt, width=12, height=10, dpi=600, units="cm")

print(cov_sex)
print(cov_age)
print(cov_wt)
```

## Model 4

2 cmp dispos. model (fixed), 1-st order 2-cmp abs., F estimated, etas estiamted for CL/F.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/26105145/>:
VC = 7.90 l, VT = 481 L, Cl = 45.3 L/h, and Q = 38.3 L/h


```{r select-model4}
mod_to_plot <- read_model(file.path(model_dir, 4))
join_df <- nm_join(mod_to_plot) 

```

### Model summary

```{r mod4-summary}
 label_df <- mod_to_plot %>% 
  param_labels() %>% 
  apply_indices() 

param_df <- mod_to_plot %>% 
  model_summary() %>% 
  param_estimates()

report_df <- inner_join(
  label_df %>% select(-param_type),
  param_df %>% select(parameter_names, estimate, stderr, fixed),
  by = "parameter_names") %>%
  mutate(estimate=round(estimate, 3)) %>%
  mutate(stderr= case_when(
             stderr == 1.00e+10 ~ NA,
             .default = stderr)) %>%
  mutate(stderr=round(stderr, 3)) 

report_df%>% knitr::kable()
```

### Plot model fits

Model predictions:

```{r model4-fits}
# Individual and population fits
fig_model_fits<- fig_model_fits_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "model_fits" , ".png"),
         plot=fig_model_fits, width=12, height=10, dpi=600, units="cm")

print(fig_model_fits)

```

### Plot GOF fits

```{r model4-gof}

fig_gof<-fig_gof_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" , "gof" , ".png"),
      plot=fig_gof, width=12, height=10, dpi=600, units="cm")

print(fig_gof) 

```

### Covariate relationships

```{r model4-cov}

idata <- distinct(join_df,ID,.keep_all = TRUE) 

idata<-idata %>%
 mutate(SEXC=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA))

etas <- c("ETA1//Eta for CL",
          "ETA2//Eta for V1",
          "ETA3//Eta for Q",
          "ETA4//Eta for V2",
          "ETA5//Eta for KA")

p_cat<-eta_cat(idata, c("SEXC//Sex"), etas)
p_cont1<-eta_cont(idata, c("AGE//Age, y"), etas)
p_cont2<-eta_cont(idata, c("WT//Weight, kg"), etas)
# cov_sex<-(p_cat[[1]]+p_cat[[2]])/(p_cat[[3]]+p_cat[[4]])/(p_cat[[5]]+plot_spacer())
# cov_age<-(p_cont1[[1]]+p_cont1[[2]])/(p_cont1[[3]]+p_cont1[[4]])/(p_cont1[[5]]+plot_spacer())
# cov_wt <-(p_cont2[[1]]+p_cont2[[2]])/(p_cont2[[3]]+p_cont2[[4]])/(p_cont2[[5]]+plot_spacer())

cov_sex<-p_cat[[1]]
cov_age<-p_cont1[[1]]
cov_wt <-p_cont2[[1]]

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_sex" , ".png"),
         plot=cov_sex, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_age" , ".png"),
         plot=cov_age, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_wt" , ".png"),
         plot=cov_wt, width=12, height=10, dpi=600, units="cm")

print(cov_sex)
print(cov_age)
print(cov_wt)
```

## Model 5

3 cmp dispos. model (fixed), 1-st order abs., F estimated, etas estimated for CL/F.
Disposition PK parameters were fixed based on <https://pubmed.ncbi.nlm.nih.gov/8533912/>:
VC = 14.6, VP1 = 66, VP2 = 608, Cl = 52.8 L/h, and Q = 102 L/h i 40.8 L/h

```{r select-model}
mod_to_plot <- read_model(file.path(model_dir, 5))
join_df <- nm_join(mod_to_plot) 

```

### Model summary

```{r mod5-summary}
 label_df <- mod_to_plot %>% 
  param_labels() %>% 
  apply_indices() 

param_df <- mod_to_plot %>% 
  model_summary() %>% 
  param_estimates()

report_df <- inner_join(
  label_df %>% select(-param_type),
  param_df %>% select(parameter_names, estimate, stderr, fixed),
  by = "parameter_names") %>%
  mutate(estimate=round(estimate, 3)) %>%
  mutate(stderr= case_when(
             stderr == 1.00e+10 ~ NA,
             .default = stderr)) %>%
  mutate(stderr=round(stderr, 3)) 

report_df%>% knitr::kable()
```

### Plot model fits

Model predictions:

```{r model5-fits}
# Individual and population fits
fig_model_fits<- fig_model_fits_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "model_fits" , ".png"),
         plot=fig_model_fits, width=12, height=10, dpi=600, units="cm")

print(fig_model_fits)

```

### Plot GOF fits

```{r model5-gof}

fig_gof<-fig_gof_fun(join_df)

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" , "gof" , ".png"),
      plot=fig_gof, width=12, height=10, dpi=600, units="cm")

print(fig_gof) 

```

### Covariate relationships

```{r model5-cov}

idata <- distinct(join_df,ID,.keep_all = TRUE) 

idata<-idata %>%
 mutate(SEXC=case_when(
             SEX == "1" ~ "Male",
             SEX == "2" ~ "Female",
             .default = NA))

etas <- c("ETA1//Eta for CL",
          "ETA2//Eta for V1",
          "ETA3//Eta for Q",
          "ETA4//Eta for V2",
          "ETA5//Eta for KA")

p_cat<-eta_cat(idata, c("SEXC//Sex"), etas)
p_cont1<-eta_cont(idata, c("AGE//Age, y"), etas)
p_cont2<-eta_cont(idata, c("WT//Weight, kg"), etas)
# cov_sex<-(p_cat[[1]]+p_cat[[2]])/(p_cat[[3]]+p_cat[[4]])/(p_cat[[5]]+plot_spacer())
# cov_age<-(p_cont1[[1]]+p_cont1[[2]])/(p_cont1[[3]]+p_cont1[[4]])/(p_cont1[[5]]+plot_spacer())
# cov_wt <-(p_cont2[[1]]+p_cont2[[2]])/(p_cont2[[3]]+p_cont2[[4]])/(p_cont2[[5]]+plot_spacer())

cov_sex<-p_cat[[1]]
cov_age<-p_cont1[[1]]
cov_wt <-p_cont2[[1]]

ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_sex" , ".png"),
         plot=cov_sex, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_age" , ".png"),
         plot=cov_age, width=12, height=10, dpi=600, units="cm")
ggsave(paste0(figure_dir, "/model", basename(mod_to_plot$absolute_model_path), "/" ,
              "cov_wt" , ".png"),
         plot=cov_wt, width=12, height=10, dpi=600, units="cm")

print(cov_sex)
print(cov_age)
print(cov_wt)
```

# Session

```{r sessioninfo}
sessionInfo()
```
